---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here:

Bin He

## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
####PUT YOUR CODE HERE
require(tidyverse)
cces %>% mutate(ideo = factor(ideo5, levels = 1:5, labels = c("Very liberal", "Liberal", "Moderate", "Conservative", "Very conservative"))) %>% 
  ggplot(aes(x = ideo)) + geom_bar(aes(fill = ideo)) + guides(fill = "none") + xlab("Ideology")
```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
####PUT YOUR CODE HERE
cces %>% mutate(
  ideo = factor(ideo5, levels = 1:5, labels = c("Very liberal", "Liberal", "Moderate", "Conservative", "Very conservative")),
  pew = factor(pew_religimp, labels = c("Very imp.", "Somewhat imp.", "Not too imp.", "Not imp."))
) %>% 
  ggplot(aes(x = pew)) + geom_bar(aes(fill = ideo)) + xlab("Importance of Religion") + scale_fill_discrete("Ideology")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
####PUT YOUR CODE HERE
my_dat <- tibble( Semester = rep(1:6, times = 3), Student = rep(c("Amanda", "Betty", "Carol"), each = 6), Grade = runif(18, min = 80, max = 100) )
ggplot(my_dat, aes(x = Semester, y = Grade)) + geom_line(aes(color = Student)) + facet_wrap(~Student)
```
